### 2013-09-27 Tex/chapters/conclusion.tex
Ausblick auf g(xi) hinzugefügt

\subsection{Outlook}
    The behavior of the normalized critical temperatures in dependence
    on \(\sigma\) of the Relative Neighborhood graph and Gabriel graph
    are qualitatively similar to each other. One could study the behavior
    of other proximity graphs like the minimum spanning tree or the
    Delaunay triangulation to examine if it is also similar.\\

>>>>

\subsection{Outlook}
    The behavior of the normalized critical temperatures in dependence
    on \(\sigma\) of the Relative Neighborhood graph and Gabriel graph
    are qualitatively similar to each other. One could study the behavior
    of other proximity graphs like the minimum spanning tree or the
    Delaunay triangulation to examine if it is also similar.\\
    Also the approach of investigating the Binder Cumulant as a function
    of the correlation length \(g(\xi)\), which is more
    sensitive detecting nonuniversalities\cite{Hartmann2013}, could be considered.
